Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-25 paper.qmd
Updated Figure 11

limits <- 1
projected_df_n <- projected_df |> select(-ID)

@@

axis_scale <- limits/6
# axis_pos <- -2/3 * limits
axis_pos <- -1

@@

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1.25, 0.1)) +
  ylim(c(-1.25, -0.5)) +
  interior_annotation("c", 
                      position = c(0.08, 0.9),
                      cex = 3)

>>>>

limits <- 0.5
projected_df_n <- projected_df |> select(-ID)

@@

axis_scale <- limits/6
# axis_pos <- -2/3 * limits
axis_pos <- -0.8

@@

five_gau_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.9, 0.1)) +
  ylim(c(-0.9, -0.5)) +
  interior_annotation("c", 
                      position = c(0.08, 0.9),
                      cex = 3)
